---
#output: word_document
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
if(!knitr::is_html_output()) options(width = 74)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RZonar

<!-- badges: start -->
<!-- badges: end -->

RZonar makes it easy to retrieve and cleanup data from the Zonar API.

## Installation

The development version of RZonar is available from GitHub. Install with:

``` r
# install.packages("remotes")
remotes::install_github("BostonPublicSchools/RZonar")
```

## Example

This is a basic example which shows you how to retrieve all schedule events for
a specified time period:

```{r example}
library(RZonar)
sched_data <- zonar_get_schedules(
  start = paste(Sys.Date(), "07:00:00"),
  end = paste(Sys.Date(), "07:15:00"))
dplyr::glimpse(sched_data[0,])
```

The data returned from the Zonar API is not always formatted conveniently. RZonar
also provides convenience functions to post-process data returned from the API:

```{r postprocess}
dplyr::glimpse(zonar_cleanup(sched_data)[0,])
```

## Documentation

All exported functions are documented and the package includes vignettes to help
you understand how the package is structured and what it is good for. On-line 
documentation can be found at  https://bostonpublicschools.github.io/RZonar/.
