---
title: "RZonar Quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

RZonar is an R package for retrieving data from the 
[Zonar API](https://support.zonarsystems.net/hc/en-us/categories/360000020371-API-Portal)


```{r, include = FALSE}
library(RZonar)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

## Capabilities and limitations

*RZonar* is not a comprehensive Zonar client, nor does it aspire to be. It currently focuses
on just a few API endpoints, including
[schedule](https://support.zonarsystems.net/hc/en-us/articles/360018372852-GPS-Schedule-Report),
[path](https://support.zonarsystems.net/hc/en-us/articles/360016205232-Export-a-Path),
[zones](https://support.zonarsystems.net/hc/en-us/articles/360018260131-List-Location-of-Interest-GPS-Zone),
[idle events](https://support.zonarsystems.net/hc/en-us/articles/360016418051-GPS-Idle-Stop-Report),
and
[assets](https://support.zonarsystems.net/hc/en-us/articles/360016149712-Get-Assets).

The *RZonar* package does not provide anything close to a 1:1 mapping to the Zonar API; if that's what
you want just use the Zonar API directly, e.g., via the [httr2](https://httr2.r-lib.org/)
package in R. Rather, RZonar offers high-level data retrieval and formatting using
the Zonar API. It aspires to be more like an R-based version of the Zonar website,
providing relatively easy access to Zonar data.

## Function naming convention

Most functions in *RZonar* are prefixed with `zonar_get`. This makes for somewhat 
verbose function names, but makes auto-completion easy in most modern editors and 
IDEs. Assuming you use [Rstudio](https://posit.co/download/rstudio-desktop/) or
similarly capable development environment you can generall just type `zonar_` and
browse the completion suggesions to find the function you are looking for.

## Time-varying and time-invariant data

Many functions provided by *RZonar* require `start` and `end` arguments. This is
your clue that the function returns time-varying data. All such arguments may be
specified as character strings formatted as `YYY-MM-DD HH:MM:SS`. For example we
can retrieve path data from 8-9 AM on December 14th 2022 like this:

```{r path_example, eval=FALSE}
library(RZonar)

paths_12.12.22 <- zonar_get_paths(
  start = "2022-12-14 08:00:00", end = "2022-12-14 09:00:00"
  )
```

Other functions that require `start` and `end` arguments (and therefore return
time-varying data) include `zonar_get_idle_events` and `zonar_get_schedules`.

Functions without `start` or `end` arguments often return time-inverient data. 
For example, we can retrieve a list of Assets (buses) like this:

```{r assets}
assets <- zonar_get_assets()
```

Not that time-invariant data *can and does change*, e.g., when a new asset is added
to the system. However the Zonar API does not allow you to retrieve time-stamped
versions, i.e. we cannot easily get the asset list as it appeared on some arbitrary
historical date.

*RZonar* does not currently provide much in the way of analysis or visualization,
so it is often convenient to use other popular R packages for that purpose.

```{r setup, messages=FALSE}
library(dplyr)
library(ggplot2)
library(sf)
```

These packages make examining, manipulating, and plotting the data returned by
*RZonar* easier:

```{r glimpse}
glimpse(assets)
```

## Using geographical information

*RZonar* typically returns geometry as Lat/Lon points or 
[well-known text](https://en.wikipedia.org/wiki/Well-known_text_representation_of_geometry)
for simplicity and to avoid additional R package dependencies.
